### 2020-12-15 README.Rmd
update readme formatting #2
update readme title headers
Update readme with sesssion info description
add place holder for BMC Biology DOI
update readme with logo?
update readme logo
update readme

@@

> Roosheel Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*.

@@

### Licenses

@@

### Session Information

>>>>

<p align="center">
  <img width="460" height="300" src="https://github.com/BradRosenbergLab/equinepbmc/blob/307dec78c39ca7dec46d7c9235574fe2db82feec/analysis/data/derived_data/horse_DNA_image.jpg/460/300">
</p>

@@

> Roosheel Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <https://doi.org/XXXX>

@@

## Licenses

@@

## Session Information

The following session information (compute environment and R/package versions) will reproduce the analysis and figures generated in the manuscript.
